Blame and Coercion: Together Again for the Second Time

### 2019-10-11 paper.tex
monoid

	Reduction \fbox{$ s_1 \longrightarrow_{D,B} s_2 $}
	\[
	\begin{array}{rclr}

@@

	Case
	\[
	\begin{array}{rclr}
	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
		\sOOreturn{v}{\kappa_1}
	}{}
	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
		\sOOreturn{v}{\kappa_2}
	}{}
	\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
		case(v,
		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
	}{}
	\end{array}
	\]

	Apply cast
	\[
	\begin{array}{rclr}
	\funrule{
		applyCast(\cOOcast{\star}{l}{\star},v)
	}{
		\rOOsucc{v}
	}{}
	\funrule{
		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
	}{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{}
	\funrule{
		applyCast(\cOOcast{P}{l}{\star},v)
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
	}{}
	\funrule{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
	}{\sidecond{P_1 \smile P_2}}
	\funrule{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{
		\rOOfail{l}
	}{\sidecond{\neg P_1 \smile P_2}}

@@

	\caption{Dynamic semantics of the \lazyD{} Blame Calculus}
	\label{machine-cekc}
\end{figure}

@@

\subsection{$Lazy UD$ Blame Calculus}

\dots

@@

\begin{theorem}[$ id $ constructs neutrals] For all $ c : T_1 \Longrightarrow 
	T_2 $
	\begin{enumerate}
		\item $ seq(id(T_1),c) = c $
		\item $ seq(c,id(T_2)) = c $
	\end{enumerate}
\end{theorem}

@@

	Reduction \fbox{$ s_1 \longrightarrow_{D,P(C)} s_2 $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redrule{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redrule{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redrule{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

@@

\subsection{$Lazy UD$ Hyper-coercion}

>>>>

	Reduction \fbox{$ s \longrightarrow_{D,B} s $}
	\[
	\begin{array}{rclr}

@@

	\fbox{$case(v, \kappa, \kappa) = s$}
	\[
	\begin{array}{rclr}
	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
		\sOOreturn{v}{\kappa_1}
	}{}
	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
		\sOOreturn{v}{\kappa_2}
	}{}
	\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
		case(v,
		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
	}{}
	\end{array}
	\]

	\fbox{$applyCast(c,v) = r$}
	\[
	\begin{array}{rclr}
	\funrule{
		applyCast(\cOOcast{\star}{l}{\star},v)
	}{
		\rOOsucc{v}
	}{}
	\funrule{
		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
	}{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{}
	\funrule{
		applyCast(\cOOcast{P}{l}{\star},v)
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
	}{}
	\funrule{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
	}{\sidecond{P_1 \smile P_2}}
	\funrule{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{
		\rOOfail{l}
	}{\sidecond{\neg P_1 \smile P_2}}

@@

	\caption{CEK abstract machine for the \lazyD{} Blame Calculus}
	\label{machine-cekc}
\end{figure}

@@

\subsection{$Lazy UD$ Blame Calculus [Jeremy]}

UNDER CONSTRUCTION

@@

\begin{proposition}[Hyper-coercions form a Monoid]
  For all $c : T_1 \Longrightarrow T_2$,
  $c_1 : T_1 \Longrightarrow T_2$,
  $c_2 : T_2 \Longrightarrow T_3$, and
  $c_3 : T_3 \Longrightarrow T_4$,
  \begin{enumerate}
  \item $seq(id(T_1),c) = c$,
  \item $seq(c,id(T_2)) = c$, and
  \item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
  \end{enumerate}
\end{proposition}

@@

	Reduction \fbox{$ s \longrightarrow_{D,P(C)} s $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redrule{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redrule{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redrule{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

@@

\subsection{$Lazy UD$ Hyper-coercion [Jeremy]}

UNDER CONSTRUCTION
